Final Project Report - An exploration of Biliary Cirrhosis and Treatments

### 2023-12-16 Submission.Rmd
Adapted code for rubric

@@

We ca see the pruned tree has cut out some leaf nodes. This would help in avoiding overfitting the model.

>>>>

## Goals

Our goal is to explore the data through multiple approaches including regression, classification and clustering. Let us frist clear some definitions and differences overall.

[Unsupervised vs Supervised learning]{.underline}

-   **Supervised Learning:** Involves training a model on a labeled dataset, where the correct answers are provided, allowing the model to learn the relationships between the input data and output labels.

-   **Unsupervised Learning:** Involves training a model on data without labeled responses, enabling the model to identify patterns and structures in the data on its own.

[Regression vs Clustering]{.underline}

-   **Regression Learning**: A type of machine learning where the model predicts a continuous output. For example, predicting house prices based on features like size and location.

-   **Classification Learning**: A type of machine learning where the model categorizes data into discrete classes. For example, determining if an email is spam or not based on its content.

@@

We ca see the pruned tree has cut out some leaf nodes. This would help in avoiding overfitting the model. As a reminder, Overfitting is when a model learns the detail and noise in the training data to the extent that it negatively impacts the performance of the model on new data.
